---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acis

<!-- badges: start -->
<!-- badges: end -->

The goal of acis is to provide wrapper functions for Applied Climate Information System (ACIS) Web Services. 

ACIS Web Services (described at <http://www.rcc-acis.org/docs_webservices.html>) are accessed by seven types of calls: station metadata (StnMeta), raw or summarized climate data for a single station for a range of dates (StnData), data for multiple stations (MultiStnData), gridded data sets (GridData & GridData2), hourly data (StnHourly), and metadata for a geographic area (General). 


## Installation

You can install the development version of acis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("brownag/rACIS")
```

## Example

See <http://www.rcc-acis.org/docs_webservices.html> for information on how to construct ACIS queries. 

The following examples demonstrate some capabilities of `acis_query()` a low-level function for constructing queries from a parameter list, and handling output types.

```{r example}
library(acis)

# ITHACA CORNELL UNIV (sid: 304174; -76.44905, 42.44915; 960m elev)
s <- 304174

# get metadata for a station
acis_query(
 "StnMeta",
 params = list(
   sids = s,
   output = 'json'
 )
)

# get average+max temperature, and precipitation for January 2020
acis_query(
  "StnData",
  params = list(
    sid = s,
    sdate = '2020-01-01',
    edate = '2020-01-31',
    elems = 'avgt,maxt,pcpn',
    output = 'csv'
  )
)

library(terra)
# CONUS NRCC Interpolated Average Monthly Temperature (June 2020)
# specify params as raw JSON, and output=image in params list
g <- acis_query(
  "GridData",
  params = list(
    params = '{"state":"me,ca,fl,wa","grid":"1","output":"image","date":"2020-6","elems":[{"name":"avgt","interval":"mly","duration":"mly","reduce":"mean"}],"image":{"proj":"lcc","overlays":["county:0.25:gray","state:0.5:black"],"interp":"cspline","width":350}}',
    output = 'image'
  )
)
plotRGB(g)
```
